Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-12 paper/paper.tex
A bit more on variance

This prediction is generally reasonably accurate, except that for very low and very high pattern
densities, we overestimate the satisfiable region. This is due to variance: although an expected
number of solutions much below one implies a high likelihood of unsatisfiability, it is not true
that a high expected number of solutions implies that any particular instance is likely to be
satisfiable---a similar behaviour is seen with random constraint satisfaction problems
\citep{Smith:1996}.

% \citep{Smith:1994}

>>>>

This prediction is generally reasonably accurate, except that for very low and very high pattern
densities, we overestimate the satisfiable region. This is due to variance: although an expected
number of solutions much below one implies a high likelihood of unsatisfiability, it is not true
that a high expected number of solutions implies that any particular instance is likely to be
satisfiable. (Consider, for example, a sparse graph which has several isolated vertices. If one
solution exists, other symmetric solutions can be obtained by permuting the isolated vertices.
Thus although the expected number of solutions may be one, there cannot be exactly one solution.) A
similar behaviour is seen with random constraint satisfaction problems
\citep{Smith:1994,Smith:1996}.
